`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-10-05 inst/manuscript/manuscript.rmd
Clarify units of the timeMin/Max parameters by switching to timeMinSec/timeMaxSec;

##Graphic Representation of Spectral Traces
In a first, graphical data analytic step of a scramblase assay-derived data 
set, fluorescent spectra or traces may be plotted in publication-appropriate
quality with acquisition time in the x- and fluorescence intensity on the y-axis
using
```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
```
and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate `wmtsa`-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`timeMin` ) and maximal (`timeMax`) time points to be
included.

@@

`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
step plots the corresponding spectral traces (Figure 1A). Note that algorithmic
alignment to the time of dithionite addition is employed (default) as well as 
custom trimming of the time axis to account for divergent acquisition 
times between experiments.
```{r, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblaseAssayTraces("inputTable.txt", timeMax = 350)
```
```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
setwd(tmpDir)
figure1 <- addpanel(
  figure = figure1,
  topPanel = 1,
  bottomPanel = 3,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblaseAssayTraces("inputTable.txt", timeMax = 350) + theme_bw())
figure1 <- addpanel(
  figure = figure1,
  topPanel = 4,
  bottomPanel = 5,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblaseAssayPlot("inputTable.txt") + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

#Conclusion
```{r, echo = FALSE, cache = TRUE}
setwd(tmpDir)
analysis_timing_n <- 100
analysis_timing_function <- function(){
  scramblaseAssayTraces(
    "inputTable.txt",
    timeMax = 350)
  scramblaseAssayPlot("inputTable.txt")
  scramblaseAssayStats("inputTable.txt")
  gc()
}
analysis_timing <- microbenchmark(
  analysis_timing_function(),
  times = analysis_timing_n)

>>>>

##Graphic Representation of Spectral Traces
In a first, graphical data analytic step of a scramblase assay-derived data 
set, fluorescent spectra or traces may be plotted in publication-appropriate
quality with acquisition time in the x- and fluorescence intensity on the y-axis
using
```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
```
and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate `wmtsa`-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`timeMinSec` ) and maximal (`timeMaxSec`) time points
to be (in seconds) included.

@@

`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
step plots the corresponding spectral traces (Figure 1A). Note that algorithmic
alignment to the time of dithionite addition is employed (default) as well as 
custom trimming of the time axis to account for divergent acquisition 
times between experiments.
```{r, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblaseAssayTraces("inputTable.txt", timeMax = 350)
```
```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
setwd(tmpDir)
figure1 <- addpanel(
  figure = figure1,
  topPanel = 1,
  bottomPanel = 3,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblaseAssayTraces("inputTable.txt", timeMaxSec = 350) + theme_bw())
figure1 <- addpanel(
  figure = figure1,
  topPanel = 4,
  bottomPanel = 5,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblaseAssayPlot("inputTable.txt") + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

#Conclusion
```{r, echo = FALSE, cache = TRUE}
setwd(tmpDir)
analysis_timing_n <- 100
analysis_timing_function <- function(){
  scramblaseAssayTraces(
    "inputTable.txt",
    timeMaxSec = 350)
  scramblaseAssayPlot("inputTable.txt")
  scramblaseAssayStats("inputTable.txt")
  gc()
}
analysis_timing <- microbenchmark(
  analysis_timing_function(),
  times = analysis_timing_n)
